Graph-based Neuron Agglomeration using 3D Skeletons

### 2017-11-10 papers/cvpr2018/0_introduction.tex
added some figures
paper: majors updates to intro/related works/conclusion

The field of connectomics is concerned with reconstructing the wiring diagram of the brain at nanometer resolutions. 
Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) has allowed neuroscientists to produce terabytes of electron micrsocopy (EM) image data every hour~\cite{hildebrand2017whole}.
Neuroscientists believe that reconstructing an entire mammilian brain at fine resolution will enable new insights into the workings of the brain~\cite{kasthuri2015saturated}. 
These observations will allow for new advancements in neuromedicine and artificial intelligence (CITE). 
Segmentation is part of this reconstruction process, assigning a unique label for every neuron in the EM image. It is not feasible for domain experts to manually segment the vast amount of 3-D image data to model an entire brain.

A significant amount of research focuses on automatic reconstruction of the neurons in EM images because of the scope and importance of the problem (ADD REFERENCES).%TODO SEVERAL REFERENCES FOR AUTOMATIC SEGMENTATIONS
All of these algorithms extract neuronal processes through the 3-D volumes using only the raw image data as input.
Oftentimes, convolutional neural networks (CNNs) predict membrane probabilities or affinities between voxels and apply simple thresholds to agglomerate the voxels into clusters~\cite{lee2015recursive,ronneberger2015u}.
These \textit{per-voxel} algorithms produce excellent results but currently fall short of complete reconstructions with error rates of approximately $X\%$. %TODO ADD ERROR RATES

\begin{figure}
	\centering
	\includegraphics[width=0.42\linewidth]{./figures/merge_candidate1.png}
	\hspace{0.085\linewidth}
	\includegraphics[width=0.42\linewidth]{./figures/intro-cube.png}
	\caption{We use 3D skeletons to combine neuron labels to full reconstructions.}
\end{figure}

Researches currently address the failures of the per-voxel algorithms by training random-forest classifiers to agglomerate an oversegmentation of voxels~\cite{nunez2014graph} (CITE NEUROPROOF). 
These classifiers take the output of the per-voxel algorithms as input and generate high-level statistics such as affinity distributions between pixel regions. 
Presently, these methods use hand-designed features despite the evidence that machine-learned features perform better~\cite{bogovic2013learned}. 
These \textit{per-supervoxel} algorithms outperform the per-voxel algorithms but still do not provide the accuracy needed for large scale reconstructions of the brain.
Additionally, these methods do not fully leverage the wealth of shape information available.  E.g., it is well known that neurons angle at less than $30$ degrees (CITE). %TODO ADD CITATION FOR NEURON SHAPES

Here we present a \textit{graph-based} strategy that builds on top of the outputs of per-supervoxel methods by taking neuronal shape properties into account. 
Similarly we take as input automatic segmentations. 
However, we focus on general neuron shapes, traversing through the label volumes to identify potential merge candidates. 
From these locations we extract machine-learned features and generate a probability that two label segments should be joined. 
We construct a graph representation of the input label volume. 
Using graph-based optimization strategies enables us to enforce global constraints that more closely match the underlying biology of the images.
Lastly, we apply a global segmentation algorithm to produce a better reconstruction.

>>>>

The field of connectomics is concerned with reconstructing the wiring diagram of the brain at nanometer resolutions. 
Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) has allowed neuroscientists to produce terabytes of electron micrsocopy (EM) image data every hour~\cite{hildebrand2017whole}.
Neuroscientists believe that reconstructing an entire mammalian brain at fine resolution will enable new insights into the workings of the brain~\cite{kasthuri2015saturated}. 
These observations will allow for new advancements in neuromedicine and artificial intelligence.

Segmenting the image stack into a label volume is a substantial component of this reconstruction process.
In a label volume, every voxel receives a segment label corresponding to a unique neuron. 
Voxels with the same label belong to the same neuron.
It is not feasible for domain experts to manually segment the vast amount of 3-D image data to model an entire brain.
Here we introduce a scalable top-down segmentation algorithm that also leverages local information.
The top-down partitioning strategy allows us to apply domain-specific constraints to the segmentation task.

A significant amount of research focuses on automatic reconstruction of the neurons in EM images~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image}. %TODO DOUBLE CHECK REFERENCES
All of these algorithms extract neuronal processes through the 3-D volumes using the raw image data as input.
Oftentimes, convolutional neural networks (CNNs) predict membrane probabilities or affinities between voxels and apply simple thresholds to agglomerate the voxels into clusters~\cite{lee2015recursive,ronneberger2015u}.
These \textit{pixel-based} algorithms produce excellent results but currently fall short of complete reconstructions with error rates of approximately $X\%$. %TODO ADD ERROR RATES

\begin{figure*}[h!]
	\centering
	\includegraphics[width=0.22\linewidth]{./figures/pipeline/image.png}
	\hspace{0.025\linewidth}
	\includegraphics[width=0.22\linewidth]{./figures/pipeline/affinities.png}
	\hspace{0.025\linewidth}
	\includegraphics[width=0.22\linewidth]{./figures/pipeline/watershed.png}
	\hspace{0.025\linewidth}
	\includegraphics[width=0.22\linewidth]{./figures/pipeline/neuroproof.png}
	\caption{An overview of an existing pipeline in segmentation for connectomics. From left to right: the original EM image data, the output of a CNN predicting voxel affinities, clustering of the affinities using a watershed algorithm, an agglomeration of the supervoxels into larger segments.}
	\label{fig:pipeline}
\end{figure*}

Researchers currently address the failures of these pixel-based algorithms by training random-forest classifiers to agglomerate an oversegmentation of voxels~\cite{nunez2014graph,10.1371/journal.pone.0125825}.
These classifiers take the output of the pixel-based algorithms as input and generate high-level statistics such as affinity distributions between pixel regions. 
Presently, these methods use hand-designed features despite the evidence that machine-learned features perform better~\cite{bogovic2013learned}. 
These \textit{region-based} algorithms outperform the pixel-based algorithms but still do not provide the accuracy needed for large scale reconstructions of the brain.

We present a \textit{segment-based} strategy that extends on the outputs of region-based methods.
We only take as input a segmentation from a previous agglomeration algorithm and not the raw image data. 
This allows us to train on connectomics datasets at a resolution and image type different than the test datasets.
We consider the 3-D skeletons of each segments as a simplification of its shape. 
We can then quickly extract a graph from the input segmentation using the skeletonization of the segments in the volume.

We add edge weights to our graph using a 3-D CNN to predict the probabilities that nearby segments belong to the same neuron.
Using a graph-based optimization strategy enables us to enforce domain-specific global constraints such as the underlying neuronal biology.
From here we apply a global partitioning algorithm that minimizes a cost function of separating adjacent nodes in the graph.

Our method takes the output of any bottom-up segmentation strategy and creates a graph on top of this segmentation. 
We enforce domain-specific global constraints by reasoning at the graph level.
This strategy scales to massive connectomics datasets and improves accuracy over existing methods.

### 2017-11-10 papers/cvpr2018/1_related_work.tex
paper: majors updates to intro/related works/conclusion

\paragraph{Voxel-based methods.} A large amount of connectomics research considers the problem of extracting segmentation information at the voxel level from the raw EM images. 
Such works focus on training 2-D convolutional neural networks to predict membrane probabilities per image slice~\cite{ciresan2012deep,jain2010boundary,amelio_segmentation,rhoananet,kaynig2015large}. 
More recent strategies augment these neural networks with the $z$-dimension creating full 3-D convolutional networks~\cite{lee2015recursive}.
Oftentimes these networks produce probabilities for the affinity between voxels rather than probabilities for a voxel belonging to a cell membrane~\cite{ronneberger2015u}. 
A sizable amount of computer vision research analyzes various hand-designed shape features for determining similarity between objects~\cite{osada2002shape} and for segmentation\cite{conners1984segmentation}. 
Currently, the random-forest classifiers used in connectomics rely on hand-designed features to make merge decisions.
Some of these features encode the distribution of probabilities that voxels along a segment boundary belong to the same neuron as their neighbors~\cite{nunez2014graph,ren2003learning}.
However, there is evidence that machine-learned features outperform hand-designed ones~\cite{bogovic2013learned}.
An extensive amount of research in computer vision, applied mathematics, and statistics evaluates the loss functions and optimizers for these networks~\cite{chatfield2014return,maas2013rectifier,nesterov1983method}.

\paragraph{Super-voxel methods.} These approaches generate probabilities that neighboring voxels belong to the same neuron.
Many algorithms work at the resulting super-voxel level and train random-forest classifiers to produce segmentations of the EM images where every unique neuron in the volume has a unique label~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image} (CITE NEUROPROOF). 
Despite the success of these classifiers, they often make mistakes based on the local information leading to errors in the segmentation. 
Proofreading methods create a ``human-in-the-loop" framework that allows users to find errors and correct them \cite{haehn2017scalable,haehn2017guided,haehn2014design,error_correction_using_CNN}.

More recently, flood-filling networks merge the process of generating voxel affinities and then producing segmentations by training an end-to-end neural network that outputs segmentations~\cite{januszewski2016flood}. 
These networks produce impressive segmentation accuracies of over $X\%$.%TODO ADD ACCURACY FOR FLOOD FILLING NETWORKS
%, they are currently too slow for large scale connectomics reconstructions.

\paragraph{Graph-based methods.} Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}. 
The multicut graph partitioning algorithm extracts segments the graph and remove edges such that there are no cycles. 
This closely resembles the biological constraint that neurons have a topological genus of zero. 
There are several useful multicut heuristics which provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis,kernighan1970efficient,keuper2015efficient}

\paragraph{Skeletonization methods.} We use a graph-based abstraction of segmentation data based on skeletonizations. 
This topic is the focus of extensive research in the fields of computer graphics, mathematics, and biomedical visualization.
%The fields of computer graphics, mathematics, and biomedical visualization produce extensive research into the skeletonization of 3D binary volumes. 
Some of the research explores topologically consistent thinning algorithms and potential medical applications of these methods~\cite{palagyi20003d,palagyi2001sequential}. 
In computer graphics, fast medial axis algorithms allow animators to quickly move characters through successive frames~\cite{baran2007automatic,bharaj2012automatically}. 
In these works, the skeleton acts as the simplest representation of a 3-D volume. 
The Tree-structure Extraction Algorithm for Accurate and Robust Skeletons (TEASER) has been used by connectomics researchers to parameterize 3-D shapes~\cite{sato2000teasar,zhao2014automatic}.

>>>>

A significant amount of research in computer vision focuses segmentation of images \cite{zaitoun2015survey}. 
Here, we review some of the most successful methods that have been applied to large-scale EM images.

\paragraph{Pixel-based methods.}

A large amount of connectomics research considers the problem of extracting segmentation information at the voxel level from the raw EM images to produce label volumes.
Some early techniques apply computationally expensive graph partitioning techniques with a single node per voxel  \cite{andres2012globally}, however these methods do not scale to terabyte datasets.
Since then, several methods train 2-D CNNs to predict membrane probabilities per image slice~\cite{ciresan2012deep,jain2010boundary,kaynig2015large,rhoananet,amelio_segmentation}. 
More recent strategies augment these neural networks with the $z$-dimension creating full 3-D CNNs~\cite{lee2015recursive,ronneberger2015u}.
Oftentimes these networks produce probabilities for the affinity between voxels, i.e., the probability that adjacent voxels belong to the same neuron.
More recently, flood-filling networks produce segmentations by training an end-to-end neural network that takes EM images to label volumes~\cite{januszewski2016flood}.
These networks produce very impressive accuracies but are much too slow to scale to larger datasets.

\paragraph{Region-based methods.}

Several of these pixel-based approaches generate probabilities that neighboring voxels belong to the same neuron.
Many algorithms build on top of these methods and train random-forest classifiers to produce segmentations of the EM images~\cite{seymour2016rhoananet,nunez2014graph,10.1371/journal.pone.0125825,parag2017anisotropic,zlateski2015image}. 
Despite the success of these classifiers, they often make mistakes based on the local information leading to errors in the segmentation. 
Additionally, many recent advancements in segmentation use artificial neural networks given the evidence that machine-learned features outperform hand-designed ones~\cite{bogovic2013learned}.
A significant amount of research focuses on the training and optimization of these deep neural networks~\cite{chatfield2014return,maas2013rectifier,nesterov1983method}.

\paragraph{Segment-based methods.}

Some limited research builds on top of the region-based methods to correct errors in the segmentation \cite{rolnick2017morphological,error_correction_using_CNN}.
Similarly, proofreading methods create a ``human-in-the-loop" framework that allows users to find errors and correct them \cite{haehn2017scalable,haehn2017guided,haehn2014design}. 
Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}. 
The multicut graph partitioning algorithm produces a set of segments where no segment contains a cycles.
This closely resembles the biological constraint that neurons have a topological genus of zero. 
Unfortunately the graph partitioning formulation is NP-Hard~\cite{demaine2006correlation}.
However, there are several useful multicut heuristics which provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis,kernighan1970efficient,keuper2015efficient}.

### 2017-11-10 papers/cvpr2018/2_method.tex
Added overview of existing methods figure
added some figures
paper: majors updates to intro/related works/conclusion

@@

From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
The nodes correspond to label segments from the segmentation with edges between segments considered for merging.
Ideally, our graph has edges corresponding to all of the segments which were erroneously split with few edges between correctly split segments.
We generate a skeleton for every segment following the intuition that a skeleton represents a simplified representation of the overall shape of an object. 
We locate merge candidates and produce corresponding edges based on these skeletons.
A CNN generates the edge weights by learning a merge function given two segments as input. 
A multicut heuristic generates a partition on the graph where nodes in the same partition are assigned the same output label. 
Thus there are three major components to our framework: skeletonization for constructing a graph, network training for determining edge weights, and graph-partitioning using a multicut heuristic algorithm. (INSERT FIGURE HERE)

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=0.42\linewidth]{./figures/skeleton1.png}
	\hspace{0.085\linewidth}
	\includegraphics[width=0.42\linewidth]{./figures/skeleton2.png}
	\caption{Two example outputs of the TEASER skeletonization algorithm.}
	\label{fig:skeletonization}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=0.42\linewidth]{./figures/merge_candidate1.png}
	\hspace{0.085\linewidth}
	\includegraphics[width=0.42\linewidth]{./figures/merge_candidate2.png}
	\caption{Two erroneously split segments that should merge together. Most segments that we want to merge have the same general structure.}
	\label{fig:merge_candidates}
\end{figure}

@@

After constructing the graph structure we apply a graph-based segmentation strategy. 
There are many formulations of graph-based optimization strategies that provide different guarantees on their output. 
Neurons in the brain should be acyclic, i.e. the output shape should have a genus of zero. 
Current connectomics agglomeration techniques do not leverage this additional information but rather consider neighboring regions in successive order without regard to loop creation. 
In our graph formulation we enforce this topological property by applying a multicut partition onto the graph that generates a \textit{forest} on the nodes. 
A forest is a partitioning of a graph into a set of trees (i.e. no segment has a cycle). 
There are several heuristics that solve the multicut problem. For our purposes we use the Kernighan-Lin algorithm~\cite{kernighan1970efficient}.
The running time of this algorithm is $\mathcal{O}(N^3)$, where $N$ is the number of nodes in the graph (DOUBLE CHECK).

>>>>

\begin{figure}[t]
	\centering
	\includegraphics[width=0.92\linewidth]{./figures/skeleton1.png}
	\includegraphics[width=0.92\linewidth]{./figures/skeleton2.png}
	\caption{Skeletons using the TEASER algorithm.}
	\label{fig:skeletonization}
\end{figure}

@@

From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
The nodes correspond to label segments from the segmentation with edges between segments considered for merging.
Ideally, our graph has edges corresponding to all of the segments which were erroneously split with few edges between correctly split segments.
We generate a skeleton for every segment following the intuition that a skeleton represents a simplified representation of the overall shape of an object. 
We locate merge candidates and produce corresponding edges based on these skeletons.
A CNN generates the edge weights by learning a merge function given two segments as input. 
A multicut heuristic generates a partition on the graph where nodes in the same partition are assigned the same output label. 
Thus there are three major components to our framework: skeletonization for constructing a graph, network training for determining edge weights, and graph-partitioning using a multicut heuristic algorithm.

@@

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=0.92\linewidth]{./figures/split_error1.png}
	\includegraphics[width=0.92\linewidth]{./figures/split_error2.png}
	\caption{Two erroneously split segments that should merge together. Most segments that we want to merge have the same general structure.}
	\label{fig:merge_candidates}
\end{figure}

@@

After constructing the graph structure we apply a graph-based segmentation strategy. 
There are many formulations of graph-based optimization strategies that provide different guarantees on their output. 
Neurons in the brain should be acyclic, i.e. the output shape should have a genus of zero. 
Current connectomics agglomeration techniques do not leverage this additional information but rather consider neighboring regions in successive order without regard to loop creation. 
In our graph formulation we enforce this topological property by applying a multicut partition onto the graph that generates a \textit{forest} on the nodes. 
A forest is a partitioning of a graph into a set of trees (i.e. no segment has a cycle). 
There are several heuristics that solve the multicut problem. For our purposes we use the greedy-additive algorithm~\cite{keuper2015efficient}.

### 2017-11-10 papers/cvpr2018/4_results.tex
paper: majors updates to intro/related works/conclusion

Table \ref{table:skeletonization} shows the results of pruning using the skeletonization heuristic.
The baseline algorithm considers all adjacent regions for merging. 
Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations.
This edge pruning is essential for the graph partitioning algorithms which have a computational complexity dependence on the number of edges (CHECK). 
Our pruning heuristic removes at least $6\times$ the number of edges between correctly split segments on all datasets, achieving a maximum removal ratio of $20\times$. 
Equally important is the number of split errors that remain after pruning.
These are the locations that we want to merge to create a more accurate reconstruction.
For every dataset, the number of positive candidates remains relatively even. 
However, since our heuristic does not enforce an adjacency constraint of two regions when constructing edges in the graph, the difference does not indicate the number of examples excluded by pruning. 
In fact, our method finds a number of examples which are non-adjacent.
Figure \ref{fig:skeleton-results} shows two example segments which are split errors.
The top example our algorithm missed but the segments are adjacent. 
The bottom example our algorithm found despite the fact that they are not adjacent.

@@

\begin{table}
	\centering
	\begin{tabular}{c c c c} \hline
	\textbf{Dataset} & \textbf{Precision} & \textbf{Recall} & \textbf{Accuracy} \\ \hline
	Kasthuri Training & & & \\
	Kasthuri Testing & & & \\
	FlyEM Vol. 1 & & & \\
	FlyEM Vol. 2 & & & \\ \hline
	\end{tabular}
	\caption{Precision and recall for the training and three test datasets.}
	\label{fig:classification}
\end{table}

Table \ref{table:classification} shows the precision and recall for all of the datasets. Our methods are more general than traditional connectomics examples allowing us to train the network on an anisotropic dataset and get impressive results on an isotropic dataset. Our initial network does not take in any image data, only the segment shapes, so we merely extract the $1200 \textrm{nm}^3$ region from any dataset and rescale as input into the neural network. For each of the tables, the top left square gives the number of segments which should merge that we predict merge. The bottom right square gives the number of segments which should not merge that we predict should not merge. The bottom left quadrant indicates the amount of false positives, candidates which we predict merge which do not. The top right quadrant gives the amount of false negatives where we predict split although the candidates should merge. Figure \ref{fig:network-results} shows the receiver operating characteristic (ROC) curve for all four datasets.

>>>>

Table \ref{table:skeletonization} shows the results of pruning using the skeletonization heuristic.
The baseline algorithm considers all adjacent regions for merging. 
Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations.
This edge pruning is essential for the graph partitioning algorithms which have a computational complexity dependence on the number of edges. 
Our pruning heuristic removes at least $6\times$ the number of edges between correctly split segments on all datasets, achieving a maximum removal ratio of $20\times$. 
Equally important is the number of split errors that remain after pruning.
These are the locations that we want to merge to create a more accurate reconstruction.
For every dataset, the number of positive candidates remains relatively even. 
However, since our heuristic does not enforce an adjacency constraint of two regions when constructing edges in the graph, the difference does not indicate the number of examples excluded by pruning. 
In fact, our method finds a number of examples which are non-adjacent.
Figure \ref{fig:skeleton-results} shows two example segments which are split errors.
The top example our algorithm missed but the segments are adjacent. 
The bottom example our algorithm found despite the fact that they are not adjacent.

@@

\begin{table}
	\centering
	\begin{tabular}{c c c c} \hline
	\textbf{Dataset} & \textbf{Precision} & \textbf{Recall} & \textbf{Accuracy} \\ \hline
	Kasthuri Training & 0.919 & 0.936 & 0.974 \\
	Kasthuri Testing & 0.737 & 0.717 & 0.907 \\
	FlyEM Vol. 1 & 0.796 & 0.478 & 0.862 \\ 
	FlyEM Vol. 2 & 0.762 & 0.422 & 0.810 \\ \hline
	\end{tabular}
	\caption{Precision and recall for the training and three test datasets.}
	\label{table:classification}
\end{table}

Table \ref{table:classification} shows the precision and recall for all of the datasets. 
Our methods are more general than traditional connectomics examples allowing us to train the network on an anisotropic dataset and get impressive results on an isotropic dataset. 
Our initial network does not take in any image data, only the segment shapes, so we merely extract the $1200 \textrm{nm}^3$ region from any dataset and rescale as input into the neural network. 
Figure \ref{fig:network-results} shows the receiver operating characteristic (ROC) curve for all four datasets.

### 2017-11-10 papers/cvpr2018/5_conclusions.tex
paper: majors updates to intro/related works/conclusion

\begin{itemize}
	\item Impact
	\item Future work
\end{itemize}

>>>>

We present a novel method for framework neuronal processes in connectomics image datasets.
We extend on top of existing region-based agglomeration strategies and show significant accuracy improvement on two datasets from two different species. 
By extracting skeletons from every segment in the input we can quickly produce a graph with $N$ nodes and $E$ weighted edges from the input. 
We populate the edge weights using a 3-D CNN that, unlike previous methods, does not use the raw image data.
Separating the neural network from the images allows us to train on anisotropic data and test on isotropic data with different sample resolution. 
This is exceptionally important in connectomics because of the extreme labor-intensive cost of manually segmenting ground truth data.

### 2017-11-10 papers/cvpr2018/paper.tex
paper: majors updates to intro/related works/conclusion

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{algpseudocode}
\usepackage{algorithmicx}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
Advancements in electron microscopy image acquisition have created massive connectomics datasets which are petabytes in size and make manual segmentation not feasible. 
Proposed methods for automatic segmentations generate super-pixel approximations of neural membranes followed by agglomeration strategies to create full neuron reconstructions. 
However, pixel-based segmentation results widely neglect global geometric properties.
We generate skeletons of membrane labels to approximate neural pathways in 3D. This allows us to efficiently apply graph-based optimization strategies and to train automatic classifiers for shape description against manually labeled ground truth. Our classifiers detect feasible and impossible neural pathways by looking at geometric properties alone, and are able to improve the segmentation labels accordingly. We demonstrate the performance of our classifiers on multiple real-world connectomics datasets with average variation of information improvement of $X\times$. We discuss our findings and provide insights to learning shape features for neuron agglomeration.
\end{abstract}

>>>>

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{algpseudocode}
\usepackage{algorithmicx}
\usepackage{siunitx}
\usepackage{float}

@@

\begin{figure}[t]\footnotesize
	\vspace{-2.04in}
	\begin{minipage}{\textwidth}
		\begin{minipage}{0.125\textheight}
			\includegraphics[width=\linewidth]{figures/schema/teaser-image.png}
			\includegraphics[width=\linewidth]{figures/schema/teaser-segmentation.png}
		\end{minipage}
		\begin{minipage}{0.24\textwidth}
			\includegraphics[width=\linewidth]{figures/schema/pre-multicut.png}
		\end{minipage}
		\begin{minipage}{0.34\textwidth}
			\includegraphics[width=\linewidth]{figures/schema/multicut-graph.png}
		\end{minipage}
		\begin{minipage}{0.24\textwidth}
			\includegraphics[width=\linewidth]{figures/schema/post-multicut.png}
		\end{minipage}
		\caption{We take as input the results of a region-based agglomeration algorithm. We extract a graph from this segmentation and apply a top-down partitioning algorithm to improve accuracy.}
		\label{fig:teaser}
	\end{minipage}
\end{figure}

%%%%%%%%% ABSTRACT
\begin{abstract}
Advancements in electron microscopy image acquisition have created massive connectomics datasets which are petabytes in size and make manual segmentation infeasible. 
Proposed methods for automatic segmentations generate super-pixel approximations of neural membranes followed by agglomeration strategies to create full neuron reconstructions. 
However, pixel-based segmentation results widely neglect global geometric properties.
We generate skeletons of membrane labels to approximate neural pathways in 3D. This allows us to efficiently apply graph-based optimization strategies and to train automatic classifiers for shape description against manually labeled ground truth. Our classifiers detect feasible and impossible neural pathways by looking at geometric properties alone, and are able to improve the segmentation labels accordingly. We demonstrate the performance of our classifiers on multiple real-world connectomics datasets with average variation of information improvement of $X\times$. We discuss our findings and provide insights to learning shape features for neuron agglomeration.
\end{abstract}
